Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-05 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added Martin Jungs comments to section 4.3, extended acknowledgement

In the following we consider a {scenario consisting of the
  SM augmented} by dimension-six operators that respect the SM gauge
group and are composed of SM fields only. Such a scenario becomes more
and more viable for two reasons. The first is the discovery of a
scalar resonance at the LHC in agreement with all requirements of the
Higgs particle in the SM. The second are the steadily rising lower
bounds on the mass of new particles reported by ATLAS and CMS in
various more or less specific models.

A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
order of the $W$-boson {mass in~\cite{D'Ambrosio:2002ex}} for vector
couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows that SM
gauge groups in conjunction with the linear representation \todo{Ask Martin,
  Oscar how to correctly phrase this} impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm
  NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
$\Lambda_{\rm NP}$ is the high-energy scale at which new physics {
is decoupled}.

Omitting for the sake of simplicity terms of order $m_\ell^2/M_{B_s}^2$ and
$m_s/m_b$, the couplings $\wilson{S,\, S'}$ can be bound quite reliably from
\cite{Alonso:2014csa}
\begin{equation}
\begin{aligned}
  \overline{\cal B}(B_s\to \bar\ell\ell) & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2
\\[0.2cm]
  - & \frac{4 m_\ell\, m_b}{M_{B_s}^2} \mbox{Re}
  \left[ (\wilson{S} + \wilson{S'})(\wilson{10} - \wilson{10'})^* \right] \,.
\end{aligned}
\end{equation}
In similar spirit, dropping terms of order $m_\ell^2/q^2$ and
$m_s/m_b$ gives
\begin{equation}
\begin{aligned}
  F_H^\ell & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2
\\[0.2cm]
  & - \frac{4 m_\ell\, m_b}{q^2} \mbox{Re}
  \left[ (\wilson{S} - \wilson{S'})(\wilson{10} + \wilson{10'})^* \right] \,.
\end{aligned}
\end{equation}

The SM gauge group does not imply any relation between $\wilson{10}$ and
$\wilson{10'}$, so they are in general additional independent parameters. Here
we find that destructive interference with contributions involving
$\wilson{10,\, 10'}$ does not significantly alter the bounds on $\wilson{S,\,
  S'}$.  The results of two fits are shown in \reffig{fig:scalar:SM-EFT}. In the
first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on
{$B \to K \bar\mu\mu$ and $B_s \to \bar\mu\mu$}. In the second fit, we allow
$\wilson[NP]{10, 10'} \ne 0$ and further include all {$B \to K^* \bar\mu\mu$}
constraints from \reftab{tab:observables}. For both fits, all six 2D marginals
of real and imaginary parts of $\wilson{S}$ vs. $\wilson{S'}$ have nearly
circular contours of equal size that contain the SM point at the 68\% level
except for $\mbox{Re}(\wilson{S})$ vs. $\mbox{Re}(\wilson{S'})$ where it is
within the 95\% credible region. The regions hardly vary between the two fits.

@@

It must be noted that the relations \refeq{eq:mEFT-constraints} are a
consequence of embedding the Higgs in a weak doublet along with the Goldstone
bosons.  For example choosing a nonlinear representation of the scalar sector
allows additional dimension-six operators in the SM-EFT, such that the couplings
$\wilson{S,S',P,P'}$ are all independent and tensor operators have nonvanishing
couplings already at dimension six \cite{Cata:2015lta}.

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  \eos~\cite{EOS}. Concerning form factor results from lattice QCD, we thank
  Chris Bouchard and Matthew Wingate for communications on their results of
  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
  factors. We thank also David Straub for his support with LCSR results of $B\to
  K^*$ form factors \cite{Straub:2015ica}.  C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}

>>>>

In the following we consider a scenario in which it is assumed that there is
a sizeable hierarchy between the electroweak scale and the new-physics 
scale, $\Lambda_{\rm NP}$, and that the SM gauge symmetries $SU(2)_L \times
U(1)_Y$ are only broken at the electroweak scale. This results in the
augmentation of the SM by dimension-six operators that respect the SM gauge
group and are composed of SM fields only. Such a scenario becomes more
and more viable for two reasons. The first is the discovery of a
scalar resonance at the LHC in agreement with all requirements of the
Higgs particle in the SM. The second is the steadily rising lower
bounds on the mass of new particles reported by ATLAS and CMS in
various more or less specific models.

A nonredundant set of dimension-six operators of this effective theory (SM-EFT),
requiring additionally the electroweak symmetry to be linearly realized,
was given in \cite{Grzadkowski:2010es}.  The matching of the SM-EFT to the
effective theory of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale
$\mu \sim m_W$ of the order of the $W$-boson mass was performed for vector
couplings $\wilson{7,\,9,\,10}$ in~\cite{D'Ambrosio:2002ex}. The matching
of tensor \refeq{eq:tensor:ops} and scalar \refeq{eq:scalar:ops} operators 
\cite{Alonso:2014csa} shows that SM gauge groups in conjunction with the 
linear representation impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $(\sim v/\Lambda_{\rm
  NP})^2 \ll 1$ where $v \propto m_W$ denotes the scale of electroweak symmetry breaking.

It must be noted that the relations \refeq{eq:mEFT-constraints} are a
consequence of embedding the Higgs in a weak doublet along with the Goldstone
bosons.  For example choosing a nonlinear representation of the scalar sector
allows additional dimension-six operators in the according effective theory, 
such that the couplings $\wilson{S,S',P,P'}$ are all independent and tensor
operators have nonvanishing couplings already at dimension six 
\cite{Cata:2015lta}.

Omitting for the sake of simplicity terms of order $m_\ell^2/M_{B_s}^2$ and
$m_s/m_b$, the couplings $\wilson{S,\, S'}$ can be bound from~\cite{Alonso:2014csa}
\begin{equation}
\begin{aligned}
  \overline{\cal B}(B_s\to \bar\ell\ell) & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2
\\[0.2cm]
  - & \frac{4 m_\ell\, m_b}{M_{B_s}^2} \mbox{Re}
  \left[ (\wilson{S} + \wilson{S'})(\wilson{10} - \wilson{10'})^* \right] \,.
\end{aligned}
\end{equation}
In similar spirit, dropping terms of order $m_\ell^2/q^2$ and
$m_s/m_b$ gives
\begin{equation}
\begin{aligned}
  F_H^\ell & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2
\\[0.2cm]
  & - \frac{4 m_\ell\, m_b}{q^2} \mbox{Re}
  \left[ (\wilson{S} - \wilson{S'})(\wilson{10} + \wilson{10'})^* \right] \,.
\end{aligned}
\end{equation}

In the SM-EFT no relations between $\wilson{10}$ and$\wilson{10'}$ arise, 
so they are in general additional independent parameters. Here
we find that destructive interference with contributions involving
$\wilson{10,\, 10'}$ does not significantly alter the bounds on $\wilson{S,\,
  S'}$.  The results of two fits are shown in \reffig{fig:scalar:SM-EFT}. In the
first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on
{$B \to K \bar\mu\mu$ and $B_s \to \bar\mu\mu$}. In the second fit, we allow
$\wilson[NP]{10, 10'} \ne 0$ and further include all {$B \to K^* \bar\mu\mu$}
constraints from \reftab{tab:observables}. For both fits, all six 2D marginals
of real and imaginary parts of $\wilson{S}$ vs. $\wilson{S'}$ have nearly
circular contours of equal size that contain the SM point at the 68\% level
except for $\mbox{Re}(\wilson{S})$ vs. $\mbox{Re}(\wilson{S'})$ where it is
within the 95\% credible region. The regions hardly vary between the two fits.

@@

@@

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgements}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  \eos~\cite{EOS}. Concerning form factor results from lattice QCD, we thank
  Chris Bouchard and Matthew Wingate for communications on their results of
  $B\to K$ \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form
  factors. We thank also David Straub for his support with LCSR results of $B\to
  K^*$ form factors \cite{Straub:2015ica}. We thank Martin Jung, David Straub
  and Danny van Dyk for comments on the manuscript. C.B. was supported by the ERC
  Advanced Grant project ``FLAVOUR'' (267104). We acknowledge the support by the
  DFG Cluster of Excellence "Origin and Structure of the Universe". The
  computations have been carried out on the computing facilities of the
  Computational Center for Particle and Astrophysics (C2PAP).
\end{acknowledgements}
